
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
\item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{
\begin{itemize}[leftmargin=*]}
    \newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}}
\newcommand{\resumeItemListStart}{
\begin{itemize}}
    \newcommand{\resumeItemListEnd}{
  \end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://max.netterberg.com/}{\Large Max Netterberg}}
  & Email : \href{mailto:max.netterberg@gmail.com}{max.netterberg@gmail.com}\\
  \href{https://max.netterberg.com/}{https://max.netterberg.com} &
  Mobile : +46 70-044 15 66 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Uppsala University}{Uppsala, Sweden}
{Masters in engineering, IT sociotechnical systems}{Aug. 2015 -- Aug. 2021}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Mentimeter AB}{Stockholm, Sweden}
{Software Engineer}{Jan. 2025 -- Aug. 2025}

\resumeItemListStart
\resumeItem{Translation project} {
  Played a big role in translating the Mentimeter platform, providing
  guidence and developed AI tools for other developers to increase
  their efficiency
}

\resumeItemListEnd

\resumeSubheading
{Mevisio AB (Netlight)}{Stockholm, Sweden}
{Project Lead \& Backend Developer}{Jan. 2023 -- Jan. 2025}
\resumeItemListStart
\resumeItem{Customer Exellence} {
  Led the backend development of the Customer Excellence Tool,
  enhancing customer data analysis and providing actionable insights.
}

\resumeItem{Knowledge Hub} {
  Developed a Knowledge Hub for accessing essential documentation,
  improving user experience and streamlining operations for the SaaS platform.
}

\resumeItem{Mevisio Platform Enhancement} {
  Contributed to the Mevisio Platform by implementing new features and
  development improvements, driving ongoing platform growth and performance.
}

\resumeItem{CI/CD Pipeline Optimization}
{Reduced the CI/CD pipeline time by 75\%, significantly accelerating
deployment processes and increasing development efficiency.}

\resumeItemListEnd

\resumeSubheading
{ABC Labs AB (Netlight)}{Stockholm, Sweden}
{Backend Developer \& DevOps Engineer, Tech Lead}{July. 2021 -- Jan. 2023}
\resumeItemListStart
\resumeItem{LIMS Integration}
{Integrated CareOS with three Laboratory Information Systems (LIMS)
and healthcare platforms, automating sample orders and result reporting.}

\resumeItem{Solution Design}
{Collaborated with developers to design integration solutions,
ensuring alignment with CareOS and laboratory requirements.}

\resumeItem{End-to-End Responsibility}
{Managed the full integration lifecycle, from requirement definition
with product owners and the laboratory to development and deployment.}

\resumeItem{Process Automation}
{Enhanced laboratory efficiency by automating manual tasks and
implementing sanity checks, reducing errors and improving turnaround times.}

\resumeItem{Event-Driven Architecture}
{Designed an event-driven system and implemented Node.js for seamless
frontend/backend integration, accelerating feature delivery.}

\resumeItem{Kubernetes Setup}
{Created and managed Kubernetes manifests for staging and production
environments, streamlining microservices deployment.}

\resumeItem{Tech Leadership}
{Mentored new developers, conducted interviews, and provided
technical support, enhancing team efficiency and meeting project deadlines.}

\resumeItem{System Scalability}
{Improved CareOS platform architecture to support high-scale lab
automation and faster sample turnaround.}

\resumeItem{Rapid Feature Delivery}
{Adapted to changing priorities, ensuring timely delivery of new
features and maintaining high system performance.}
\resumeItemListEnd

\resumeSubheading
{Sun Labs Nordic AB}{Uppsala, Sweden}
{Software Engineer}{July. 2020 -- Mar. 2021}
\resumeItemListStart
\resumeItem{React Native Migration}
{Led the migration of a React web application to a React Native
  mobile app, enabling access to native features like the camera and
  notifications. Added functionalities such as push notifications and
QR code scanning.}
\resumeItemListEnd

\resumeSubheading
{Wines We Want SARL}{France}
{Software Engineer}{Apr. 2020 -- Dec. 2020}
\resumeItemListStart
\resumeItem{Website Modernization, Vue}
{Redesigned the webshop’s tech stack, transitioning from a monolithic
  PHP backend to a modular frontend/backend architecture. Developed a
Vue.js single-page application with a RESTful API connected to a MySQL database}
\resumeItem{API Design \& Architecture}
{Led the API design, ensuring smooth data flow between the backend
  and frontend. Delivered a new platform structure, enhancing feature
scalability and improving customer experience.}
\resumeItemListEnd

\resumeSubheading
{Prorenata AB}{Stockholm, Slussen}
{Software Engineer}{Jul. 2020 -- Dec. 2020}
\resumeItemListStart
\resumeItem{Playwright, E2E Testing}
{Led the successful integration of a new end-to-end testing framework
  for Prorenata, enhancing their CI/CD pipeline and enabling
  test-driven development, while providing tailored solutions and
collaborating closely with the frontend lead and QA team.}
\resumeItemListEnd

\resumeSubheading
{Cepheid AB}{Stockholm, Solna}
{Software Engineer}{Feb. 2020 -- Jul. 2020}
\resumeItemListStart
\resumeItem{Angular, Java Spring Boot}
{Contributed to upgrading Cepheid's C360 system by porting it to the
  latest Angular version, integrating it with a Java Spring Boot API,
  and was highly valued for his teamwork, proactive approach, and
knowledge sharing.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{
  \textbf{Languages}{: Typescript, Rust, Golang, Kotlin, Ruby, Javascript}
  \hfill
}
\item {
  \textbf{Technologies}{: AWS, React, Vue, Kafka, GCE, CQRS, gRPC,
    Websockets, Postgres, OIDC, Rest API, Docker, Kubernetes, Node.js,
    RabbitMQ, Redis, Terraform, Github, JIRA, React Native, Solid,
    Angular, Deno, Cloudflare
  }
}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Side Projects}
\resumeSubHeadingListStart
\resumeSubItem{Neon Programming language}
{
  My own programming language.
  \href{https://github.com/redsuperbat/neon}{Github Link}
}
\resumeSubItem{Code spellchecker}
{
  Spellchecker utilizing the language server protocol to spellcheck code
  \href{https://github.com/redsuperbat/rustproof}{Github Link}
}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
